\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Matthew Huynh} \\ \vspace{1pt}
    \small (416)-433-5784 $|$ \href{mailto:huynhmatthew0@gmail.com}{\underline{huynhmatthew0@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/matthew-huynh/}{\underline{linkedin.com/in/Matthew-Huynh}} 
    % \href{https://github.com/M9Huynh}{\underline{github.com/M9Huynh}}
\end{center}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Consultant}{Jan. 2025 -- Aug. 2025}
      {BDO Canada -- Credits \& Incentives}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Draft technical reports for SR\&ED and Clean Economy Investment Tax Credits, primarily focusing of software development and engineering projects for eligibility.}
        \resumeItem{Collaborate with clients across various industries to document technological advancements and challenges in their R\&D initiatives.}
    \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant}{Sep. 2021 -- Present}
      {McMaster University -- ENG 1P13, ENG 2PX3, INNOVATE 2Z03, ENGMGNT 4A03}{Hamilton, ON}
      \resumeItemListStart
        \resumeItem{Guided 80+ undergraduate students through engineering design and programming fundamentals, providing technical mentorship and personalized feedback.}
        \resumeItem{Evaluated and supervised engineering projects using Autodesk Inventor, Python, and Quanser, helping students develop innovative solutions to real-world problems.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{May 2023 -- Aug. 2023}
      {Royal Bank of Canada -- Ojo Canada}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Applied an agile development methodology to successfully create a React Native application using TypeScript for our front-end development.}
        \resumeItem{Assisted in the initial setup for push notifications using Firebase Cloud Messaging, enhancing user engagement and communication within the app.}
        \resumeItem{Effectively integrated our application with Google Analytics to allow for data-driven decision making and providing valuable insights for future improvements.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{May 2022 -- Aug. 2022}
      {Royal Bank of Canada -- Amplify}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Collaborated with a cross-functional team of \textbf{4} under SmartReno to address challenges of creating a stress-free renovation journey for Canadian homeowners.}
        \resumeItem{Designed the user interface of our web application using industry standard technologies such as React.js, Axios, and Material UI, ensuring an appealing user experience.}
        \resumeItem{Conducted in-depth market research, user interviews and competitive analysis to inform the creation of multiple user personas in which our application could be tailored to.}
    \resumeItemListEnd

    \resumeSubheading
      {Analyst}{May 2021 -- Aug. 2021}
      {Grant Thornton - R\&D and Government Incentives}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Collaborated closely with a multidisciplinary team of engineers and accountants to assess client's innovated and experimental processes, aimed at resolving technological uncertainties.}
        \resumeItem{Assisted in documenting and communicating project details during client meetings. Prepared working papers and CRA (Canada Revenue Agency) tax documents, facilitating claims of up to \textbf{35\%} of the client's annual expenditure in government incentives.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Paddle Hand Tracker} $|$ \emph{Python, OpenCV}}{}
        \resumeItemListStart
          \resumeItem{Python program that utilizes \textbf{Open-CV} to supplement athlete training for dragon boat form when paddling with \textbf{90\%+} accuracy.}
          \resumeItem{Developed version control skills using \textbf{Git} by keeping everything up-to-date and gained further understanding of CI/CD pipelines through this project.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: React.js, React Native, Jest, JUnit 5, Material-UI} \\
     \textbf{Developer Tools}{: Git, Jira, Linux, Firebase, Google Analytics} \\
    }}
 \end{itemize}

    %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Sep. 2020 -- Apr. 2026}
      {Bachelor of Software Engineering and Management}{Hamilton, ON}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}